\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Intro to CV}
\author{TJHSST Computer Vision Club }
\date{September 5th, 2017}

\begin{document}

\maketitle

\section{Format}
Computer Vision Club

Welcome to the TJHSST Computer Vision Club! This club will occur every week Wednesday B Block. We strongly encourage you to attend as frequently as possible, as every week, we will be doing the following:


\begin{itemize}
  \item Constructive lecture (10-15 minutes)

  \item Questions/Answer Session (5 minutes)
  \item Related Lab (20 minutes)
  \item Monthly Competition (5-10 minutes, and continued for home)


\end{itemize}


\section{Competitions}

Each month, a monthly competition will be posted on the TJHSST Computer Vision  Club website. Students can email their code to tjcomputervision@gmail.com, and the team/individual with the most effective code will receive a prize. This way, students are motivated and excited to apply their newfound knowledge towards real life problems. We have decided that we will have a total of 8 different competitions related to the subject matter of that month.

\section{Website}
Most of our club’s information, including the lectures, powerpoints, and various other documents, can be found online, at TJComputervision.com (will be created). This way, all students will be able to be kept together even if they cannot come on a certain day. Below is our schedule till winter break. During winter break, large updates will be made to the website and competition structure, and afterwards, we will be offering a new competition via our website.

\section{Schedule}
Below is our tentative schedule, till Winter Break
\begin{itemize}
  \item Wednesday, September 13th: Introduction to Club
  \item Wednesday, September 20th: Linear Algebra/Introduction to Transformations
  \item Wednesday, September 27th: Introduction to OpenCV Python
  \item Wednesday, October 4th: Image File Manipulation Part 1
  \item Wednesday, October 18th: Image File Manipulation Part 2

  \item Wednesday, October 25th: Image Edge/Corner Detection
  \item Wednesday, November 1st: Optical Flow
 
  \item Wednesday, November 15th: Interpolation

  \item Wednesday, November 29th: Super Resolution

 \item Wednesday, December 6th: Morphology

\item Wednesday, December 13th: Hough Transform (Example Lecture Notes/Powerpoint included)

\end{itemize}


\section{Resources}
Attached, you may find an example lecture, written in the same Latex format, as well as an example powerpoint to demo how we plan to teach the members of our unique club.












\end{document}
